Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-02-02 Documents/M1/realizableFermionicM1/manuscript.tex
Updates to paper
modifications to Lemma 1.  Minor edits to DG discretization.
Added the plots of Mab.
Reworked title
Added lemma on correction step

\usepackage{lineno,hyperref}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\modulolinenumbers[5]
\hypersetup{
  bookmarksnumbered = true,
  bookmarksopen=false,
  pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
  pdffitwindow=true,      % window fit to page when opened
  pdfnewwindow=true, % links in new window
  colorlinks=true,           % false: boxed links; true: colored links
  linkcolor=blue,            % color of internal links
  citecolor=magenta,    % color of links to bibliography
  filecolor=magenta,     % color of file links
  urlcolor=cyan              % color of external links
}

@@

@@

\title{Realizability-Preserving Two-Moment DG Method for Fermionic Transport \tnoteref{ldrd-support}}
\tnotetext[ldrd-support]{This research is sponsored by ...}

@@

\input{sections/intro}
\input{sections/model}
\input{sections/MomentsRealizability}
\input{sections/IMEX}
\input{sections/DGmethod}
\input{sections/DGIMEXscheme}
\input{sections/limiter}
\input{sections/numerical}
\input{sections/conclusion}
%\input{sections/appendix}
\clearpage

>>>>

\usepackage{lineno,hyperref}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{subcaption}

\modulolinenumbers[5]
\hypersetup{
  bookmarksnumbered = true,
  bookmarksopen=false,
  pdfborder=0 0 0,         % make all links invisible, so the pdf looks good when printed
  pdffitwindow=true,      % window fit to page when opened
  pdfnewwindow=true, % links in new window
  colorlinks=true,           % false: boxed links; true: colored links
  linkcolor=blue,            % color of internal links
  citecolor=magenta,    % color of links to bibliography
  filecolor=magenta,     % color of file links
  urlcolor=cyan              % color of external links
}

@@

\newtheorem{define}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{rem}{Remark}
\newtheorem{theorem}{Theorem}

@@

\title{Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}}
\tnotetext[support]{This research is sponsored by ...}

@@

\input{sections/intro}
\input{sections/model}
\input{sections/realizability}
\input{sections/dg}
\input{sections/imex}
\input{sections/DGIMEXscheme}
\input{sections/limiter}
\input{sections/numerical}
\input{sections/conclusion}
%\input{sections/appendix}
\clearpage

### 2018-02-02 Documents/M1/realizableFermionicM1/sections/realizability.tex
Added lemma on correction step

For the realizability-preserving scheme, we state some additional results.  
\begin{lemma}
  Let $\big\{\cJ_{a},\vect{\cH}_{a},\vect{\cK}_{a}\big\}$ be defined as in Eq.~\eqref{eq:angularMoments} with distribution function $f_{a}(\omegaNu)\in[0,1]\,\forall\,\omegaNu\in\bbS^{2}$.  
  Similarly, let $\big\{\cJ_{b},\vect{\cH}_{b},\vect{\cK}_{b}\big\}$ be moments of a distribution function $f_{b}\in[0,1]\,\forall\,\omegaNu\in\bbS^{2}$.  
  Let $\Phi^{\pm}(\vect{\cM})=\f{1}{2}\big(\vect{\cM}\pm\widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cM})\big)$, where $\widehat{\vect{e}}\in\bbR^{3}$ is an arbitrary unit vector, and $\widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cM})=\big(\widehat{\vect{e}}\cdot\vect{\cH},\widehat{\vect{e}}\cdot\vect{\cK}\big)^{T}$.  
  Then
  \begin{equation*}
    \vect{\cM}_{ab} = \big(\cJ_{ab},\vect{\cH}_{ab}\big)^{T} \equiv \Phi^{+}(\vect{\cM}_{a})+\Phi^{-}(\vect{\cM}_{b})\in\cR.
  \end{equation*}
\end{lemma}
\begin{proof}
  It is straightforward to rewrite the components of $\vect{\cM}_{ab}$ as
  \begin{equation*}
    \cJ_{ab}=\f{1}{4\pi}\int_{\bbS^{2}}f_{ab}(\omegaNu)\,d\omegaNu
    \quad\text{and}\quad
    \vect{\cH}_{ab}=\f{1}{4\pi}\int_{\bbS^{2}}f_{ab}(\omegaNu)\,\vect{\ell}(\omegaNu)\,d\omegaNu,
  \end{equation*}
  where $f_{ab}(\omegaNu)=\theta\,f_{a}+(1-\theta)\,f_{b}$ and $\theta(\omegaNu)=(1+\widehat{\vect{e}}\cdot\vect{\ell}(\omegaNu))/2\in[0,1]$.  
  Then, since $f_{ab}(\omegaNu)\in[0,1]\,\forall\,\omegaNu\in\bbS^{2}$, we have from Lemma~\ref{lem:MomentRealizable} that $\vect{\cM}_{ab}\in\cR$.  
\end{proof}
\begin{lemma}
  Let $\vect{\cM}_{a}=(\cJ_{a},\vect{\cH}_{a})^{T}\in\cR$ and $\alpha>0$.  
  Let $\vect{\cM}_{b}=(\cJ_{b},\vect{\cH}_{b})^{T}$ satisfy
  \begin{equation*}
    \vect{\cM}_{b}=\vect{\cM}_{a}+\alpha\,\vect{\cC}(\vect{\cM}_{b}), 
  \end{equation*}
  where $\vect{\cC}(\vect{\cM})$ is the collision term in Eq.~\eqref{eq:collisionTermMoments}.  
  Then $\vect{\cM}_{b}\in\cR$.  
\end{lemma}

\begin{lemma}
  For any $\vect{\cM}_{a}=(\cJ_{a},\vect{\cH}_{a})^{T}\in\cR$ and $\alpha>0$,
  \begin{equation*}
    \vect{\cM}_{b}\equiv\vect{\cM}_{a}+\alpha\,\vect{\cC}(\vect{\cM}_{b})\in\cR
  \end{equation*}
  where $\vect{\cC}(\vect{\cM})$ is the collision term in Eq.~\eqref{eq:collisionTermMoments}.
\end{lemma}

@@

>>>>

For the realizability-preserving scheme, we state some additional results.  
\begin{lemma}
  Let $\big\{\cJ_{a},\vect{\cH}_{a},\vect{\cK}_{a}\big\}$ be defined as in Eq.~\eqref{eq:angularMoments} with distribution function $f_{a}(\omegaNu)\in[0,1]\,\forall\,\omegaNu\in\bbS^{2}$.  
  Similarly, let $\big\{\cJ_{b},\vect{\cH}_{b},\vect{\cK}_{b}\big\}$ be moments of a distribution function $f_{b}\in[0,1]\,\forall\,\omegaNu\in\bbS^{2}$.  
  Let $\Phi^{\pm}(\vect{\cM})=\f{1}{2}\big(\vect{\cM}\pm\widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cM})\big)$, where $\widehat{\vect{e}}\in\bbR^{3}$ is an arbitrary unit vector, and $\widehat{\vect{e}}\cdot\vect{\cF}(\vect{\cM})=\big(\widehat{\vect{e}}\cdot\vect{\cH},\widehat{\vect{e}}\cdot\vect{\cK}\big)^{T}$.  
  Then
  \begin{equation*}
    \vect{\cM}_{ab} = \big(\cJ_{ab},\vect{\cH}_{ab}\big)^{T} \equiv \Phi^{+}(\vect{\cM}_{a})+\Phi^{-}(\vect{\cM}_{b})\in\cR.
  \end{equation*}
\end{lemma}
\begin{proof}
  It is straightforward to rewrite the components of $\vect{\cM}_{ab}$ as
  \begin{equation*}
    \cJ_{ab}=\f{1}{4\pi}\int_{\bbS^{2}}f_{ab}(\omegaNu)\,d\omegaNu
    \quad\text{and}\quad
    \vect{\cH}_{ab}=\f{1}{4\pi}\int_{\bbS^{2}}f_{ab}(\omegaNu)\,\vect{\ell}(\omegaNu)\,d\omegaNu,
  \end{equation*}
  where $f_{ab}(\omegaNu)=\theta\,f_{a}(\omegaNu)+(1-\theta)\,f_{b}(\omegaNu)$ and $\theta(\omegaNu)=(1+\widehat{\vect{e}}\cdot\vect{\ell}(\omegaNu))/2\in[0,1]$.  
  Then, since $f_{ab}(\omegaNu)\in[0,1]\,\forall\,\omegaNu\in\bbS^{2}$, we have from Lemma~\ref{lem:MomentRealizable} that $\vect{\cM}_{ab}\in\cR$.  
\end{proof}

\begin{lemma}
  Let $\vect{\cM}_{a}=(\cJ_{a},\vect{\cH}_{a})^{T}\in\cR$ and $\alpha>0$.  
  Let $\vect{\cM}_{b}=(\cJ_{b},\vect{\cH}_{b})^{T}$ satisfy
  \begin{equation*}
    \vect{\cM}_{b}=\vect{\cM}_{a}+\alpha\,\vect{\cC}(\vect{\cM}_{b}), 
  \end{equation*}
  where $\vect{\cC}(\vect{\cM})$ is the collision term in Eq.~\eqref{eq:collisionTermMoments}.  
  Then $\vect{\cM}_{b}\in\cR$.  
  \label{lem:implicitStep}
\end{lemma}

%\begin{lemma}
%  For any $\vect{\cM}_{a}=(\cJ_{a},\vect{\cH}_{a})^{T}\in\cR$ and $\alpha>0$,
%  \begin{equation*}
%    \vect{\cM}_{b}\equiv\vect{\cM}_{a}+\alpha\,\vect{\cC}(\vect{\cM}_{b})\in\cR
%  \end{equation*}
%  where $\vect{\cC}(\vect{\cM})$ is the collision term in Eq.~\eqref{eq:collisionTermMoments}.
%\end{lemma}

@@

\begin{lemma}
  Let $\vect{\cM}_{a}$ and $\alpha$ be given as in Lemma~\ref{lem:implicitStep}, and let $\vect{\cM}_{b}$ satisfy
  \begin{equation*}
    \vect{\cM}_{b}=\vect{\cM}_{a}+\alpha\,\vect{\cD}\,\vect{\cC}(\vect{\cM}_{b}),    
  \end{equation*}
  where $\vect{\cD}$ and $\vect{\cC}(\vect{\cM})$ are given by Eq.~\eqref{eq:collisionTermMoments}.  
  Then $\vect{\cM}_{b}\in\cR$.  
  \label{lem:correctionStep}
\end{lemma}

\begin{proof}
  The proof follows along the same lines as the proof of Lemma~\ref{lem:implicitStep}.  
\end{proof}
